---
title: "Day 5: Wrapping Up"
subtitle: ""
author: ""
institute: "DIMA Units of Regional Bureaux: EHAGL, SA and WCA"
date: "18 February 2022"
output:
  xaringan::moon_reader:
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
      ratio: 16:9
    css: ["unhcr-slides.css", "unhcr-slides-fonts.css"]
    includes:
      in_header: header.html    
---
layout: true

<div class="my-footer"><span></span></div> 

<style type="text/css">

h2 {
  text-align: center;
  position: fixed;
  top: 50%;
  left: 50%;
  transform: translate(-50%, -50%);
}
}
</style>

```{r setup, include=FALSE}
extrafont::loadfonts(quiet=TRUE)
options(scipen = 999) # turn-off scientific notation like 1e+48

options(htmltools.dir.version = FALSE)
library(knitr)
knitr::opts_chunk$set(cache = TRUE, 
                      warning = FALSE, 
                      message = FALSE, 
                      dpi = 180,
                      fig.retina = 3,
                      fig.width = 6,
                      fig.asp = 0.618
                      )

library(fontawesome)

```

---
# Today will be about:

* Recap of Last 4 Days

* Small Things to Know
  + R Coding Style
  + Strings and Country Names

* Not Yet Asked Questions

* Potential Areas to Cover in the Future

* Building Community

* Feedback

---
# Recap of Last 4 Days

* Introduction

* Basics and Data Import

* Data Manipulation

* R Markdown

---
# Small Things to Know

#### R Coding Style: Notation and Naming (Reference: [R Coding Style](https://rstudio-pubs-static.s3.amazonaws.com/390511_286f47c578694d3dbd35b6a71f3af4d6.html#))

##### File names

File names should be meaningful and end in **.R**.

```{r, eval=FALSE}
# Good
 fit-models.R
 utility_functions.R

# Bad
 foo.r
 stuff.r

```

If files need to be run in sequence, prefix them with numbers:

```{r, eval=FALSE}
0-download.R
1-parse.R
2-explore.R

```

---
# Small Things to Know

#### R Coding Style: Notation and Naming (Reference: [R Coding Style](https://rstudio-pubs-static.s3.amazonaws.com/390511_286f47c578694d3dbd35b6a71f3af4d6.html#))

##### Object names

.pull-left[
Variable and function names should be lowercase. Use an underscore (_) to separate words within a name. Generally, **variable** names should be **nouns** and **function** names should be **verbs**. 

```{r, eval=FALSE}
# Good
day_one
day_1
dayOne

# Bad
first_day_of_the_month
dayone
djm1

```
]

.pull-right[
Where possible, avoid using names of existing functions and variables. Doing so will cause confusion for the readers of your code.

```{r}
# Bad
T <- FALSE
c <- 10
mean <- function(x) sum(x)

```
]

---
# Small Things to Know

#### R Coding Style: Syntax (Reference: [R Coding Style](https://rstudio-pubs-static.s3.amazonaws.com/390511_286f47c578694d3dbd35b6a71f3af4d6.html#))

##### Spacing

.pull-left[
Place spaces around all infix operators (=, +, -, <-, etc.). The same rule applies when using = in function calls. Always put a space after a comma, and never before (just like in regular English).

```{r, eval=FALSE}
# Good
average <- mean(feet / 12 + inches, na.rm = TRUE)

# Bad
average<-mean(feet/12+inches,na.rm=TRUE)

```
]

.pull-right[
There's a small exception to this rule: :, :: and ::: don't need spaces around them.

```{r, eval=FALSE}
# Good
x <- 1:10
base::get

# Bad
x <- 1 : 10
base :: get

```
]


---
# Small Things to Know

#### String Problem of Country Names

* Recommend to use country code. Use consistent codes of one standard only.

countryofasylum | countryoforigin | value
----------------|----------|--------
Democratic Republic of the Congo | Cote d'Ivoire | 345
Dem. Rep. of the Congo | Côte d'Ivoire | 125
DRC | Palestine | 453
DRC | State of Palestine | 4675

* Encoding issue

---
## Not Yet Asked Questions

---
## Potential Areas to Cover in the Future

---
## Building Community

---
## Feedback

