---
author: "Pan-Africa DIMA Units"
date: "`r format(Sys.Date(),  '%d %B %Y')`"
output:
  unhcrdown::docx_simple
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.cap = TRUE, fig.width = 6.27)
library(officedown)
library(officer)
library(tidyverse)
library(dplyr)
library(readr)
library(knitr)
library(flextable)

asr <- read_csv("C:/Users/FEITOSAV/OneDrive - UNHCR/Documents/R/panafrican-dima-r-training/dataviz_markdown/markdown/data/asr_demographics.csv")

asr_year <- "2019" # Created this object to facilitate filtering in next reports

asr_total <- sum(asr$total)

asr_top5 <- asr %>%
  filter(year == asr_year) %>% # Link with object above
  group_by(asylum_name) %>% # Grouped by country of asylum
  select(c("asylum_name", "total")) %>% # Selected specific columns from the original data frame
  summarize(total_sum = sum(total)) %>%
  arrange(desc(total_sum)) %>%
  head(5)

```

---
title: "Population Statistics `r asr_year`"
---

# Methodology

Let's say we are drafting a report that will be updated every quarter. The methodology section will not change substantially. We can leave the text as it is, but adding dynamic parts. For example: this report analyzes data on UNHCR's population of concern in the year **`r asr_year`**. This number will be updated whenever we filter a different year in the object above.

## Basic commands

In this subsection, we will introduce some basic commands for reports in markdown.

### Style of text

We can customize the style of the text. 
**Bold text** 
*Italic text* 
***Bold and italic text*** 

### Quotes
::: {custom-style="Quote"}

"It is further proof that refugee movements and the broader issue of migration of populations ... is a global challenge that cannot be confined to a few countries."

:::

**Filippo Grandi**

Footnotes are also included and will be added automatically to the bottom of the page like the following ones. This is a footnote^[Text of the footnote], it can include anything and can also be stylize UNHCR^[The **United Nations** High Commissioner for Refugees <https://www.unhcr.org/>]

### Lists

Lists also are automatic but they will need extra manual tweaking if you want to apply a more adapted paragraph style with less spacing. This apply for both ordered and unordered lists.

* item 1
* item 2
* item 3

## Tables

Tables will come with a default style. More advanced layout can be achieved using the [flextable](https://ardata-fr.github.io/flextable-book/index.html) package. Like the lists there is a built-in paragraph style if you want to improve the look and feel of your tables.

```{r, echo=FALSE, message=FALSE, warning=FALSE, tab.cap="Population of Concern by Country of Asylum"}
head(asr_top5)
```

<br>

\newpage

# Plots

Creating plots in R is an exciting universe in itself. Let's analyze the code below and reverse-engineer the main elements to consider when creating a graph with R.


```{r, echo=FALSE, message=FALSE, warning=FALSE, results = 'hide'}
library(ggplot2)
library(unhcrthemes)
library(scales)

column_graph <- ggplot(asr_top5, aes(asylum_name, total_sum)) +
  geom_col(fill = unhcr_pal(n = 1, "pal_blue"))

column_graph
```

